WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-03 paper/reviews_ds.Rmd
I think it is important to stress that not only the same code but the same data are used. I see the main difference in whether the same or new data are used.

> Throughout this paper, we adhere to the definition of open science as
"the practice of science in such a way that others can collaborate and contribute,
where research data, lab notes and other research processes are freely available,
under terms that enable reuse, redistribution and reproduction of the research and its underlying data and methods" [@vicente-saezOpenScienceNow2018].  
[...] reproducibility can be defined as "re-performing the same analysis with the same code using a different analyst",
and replicability as "re-performing the experiment and collecting new data" [@patilVisualToolDefining2019].

>>>>

> Throughout this paper, we adhere to the definition of open science as
"the practice of science in such a way that others can collaborate and contribute,
where research data, lab notes and other research processes are freely available,
under terms that enable reuse, redistribution and reproduction of the research and its underlying data and methods" [@vicente-saezOpenScienceNow2018].  
[...] reproducibility can be defined as "re-performing the same analysis with the same code and the same data using a different analyst",
and replicability as "re-performing the experiment and collecting new data" [@patilVisualToolDefining2019].
